\documentclass{article}
\usepackage[utf8]{inputenc}

\title{CS 6000 Journal 7}
\author{David Stout}
\date{October 2018}

%\usepackage{natbib}
%\usepackage{graphicx}

\begin{document}

\maketitle

\section{Process and Learning}
I have found that my serious health issues these last two weeks have truly impeded my ability to do the work I
needed to do. Between the frequent doctor visits and the hospital stays, I have had very little time to devote
to my school work and research. But luckily I have found out that I have a better support system than I had 
believed before, I just need to ask for help and I can get it.

In writing the survey paper, I found that it was very important to get feedback from other people as I go. The 
paper is so different than anything I have ever written before that I struggled a lot with just getting into the
groove of writing a more technical paper. Trying to tell a story, while remaining professional and technical was
something that I had a hard time doing. I found myself constantly inserting my opinions and being more 
colloquial instead of formal. I was glad to have my advisor to help point out the things that I was doing that 
needed serious work. 

On the more technical side, I had to learn how to import packages into Latex to accomplish some of the things
that I wanted to do, like have verbatim code side by side in a figure. I also learned how to write my own
functions in Latex to accomplish some more little things, like being able to write keywords in the appropriate
IEEE format. I am enjoying learning how to use Latex better and am beginning to feel more comfortable with
writing a scientific paper. I feel that as I practice more and more, then I will truly begin to enjoy the
process as much as I have enjoyed the process of other less formal writing.


\end{document}
